---
title: "attrition Problem"
author: "Jaclyn A Coate"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::include_graphics("/Users/Jaco/Desktop/SMU/Fall2019/DS_6306_Doing_Data_Science/Unit_14CaseStudy2")
#, results='hide'
```

```{r environment libraries, echo=FALSE}
library(tidyverse)
library(corrplot)
library(mlbench)
library(caret)
library(skimr)
library(mice)
library(purrr)
library(ggplot2)
library(ggthemes)
#install.packages("cowplot")
library(cowplot)
library(class)
library(e1071)
```

# Attrition Model

# Exploratory Data Analysis
- Correlation
- Trends
- Causation

***
## Steps For EDA w/ Large Number of Categories / Continuous Variables
1. Check for NAs
2. Get rid of zero value variables (ones that only have one value).
3. Use common sense! (variables that don't makes sense remove from your list of variables)
    - e.g. ID, Employee Number
4. Check and make sure categorical variables are stored as factors.
    - e.g. Make sure all variables are categorized correctly - categorical (stock options) or numeric
5. Storing all level numeric variables as factors
    - e.g. Job Level, College, etc.
6. Checking for highly correlated numeric variables
    - Highly correlated values can weaken the model.
    - e.g. Monthly Salary, Weekly Salary, they say the same thing and would be highly correlated
7. Numeric | Categorical
8. Categorical | Categorical
9. KNN Model Variables to Reduce

```{r data, results='hide'}
frito <- read.csv("https://raw.githubusercontent.com/JaclynCoate/MDS-6306-Doing-Data-Science-Fall-2019/Master/Unit%2014%20and%2015%20Case%20Study%202/CaseStudy2-data.csv", header = TRUE, strip.white=TRUE)
frito
invisible(ncol(frito))
invisible(skim(frito))
```

```{r, echo=FALSE}
#frito
#data(frito)
#head(frito)
#length(frito)
#skim(frito)

#Categorical:
# "Attrition", "Department", "BusinessTravel", "EducationField", "Gender", "JobRole", "MaritalStatus", "Over18", "OverTime"

# Level
# "JobInvolvement", "EnvironmentSatisfaction", "Education", "JobLevel", "JobSatisfaction", "PerformanceRating", "RelationshipSatisfaction", "StockOptionLevel", "WorkLifeBalance"

#Continuous: 
# "Age", "DailyRate", "DistanceFromHome", "EmployeeCount", "HourlyRate", "MonthlyIncome", "MonthlyRate", "NumCompaniesWorked", "StandardHours" "PercentSalaryHike", "TotalWorkingYears", "TrainingTimesLastYear", "YearsAtCompany", "YearsInCurrentRole", "YearsSinceLastPromotion", "YearsWithCurrManager"

# All Variables
# "Attrition", DailyRate", "Department", "DistanceFromHome", "Education", "EducationField", "EmployeeCount", "EnvironmentSatisfaction", "Gender", "HourlyRate", "JobInvolvement", "JobLevel", "JobRole", "JobSatisfaction", "MaritalStatus", "MonthlyIncome",  "MonthlyRate", "NumCompaniesWorked", "Over18", "OverTime", "PercentSalaryHike", "PerformanceRating", "RelationshipSatisfaction", "StandardHours", "StockOptionLevel", "TotalWorkingYears", "TrainingTimesLastYear", "WorkLifeBalance", "YearsAtCompany", "YearsInCurrentRole", "YearsSinceLastPromotion", "YearsWithCurrManager"
```

***
### 1. Missing data evaluation {data-background=""}
- No missing values 
- Continue w/ exploratory data analysis

```{r NA eval}
md.pattern(frito)
```

***
### 2. Dropping all zero variance variables
- Drop Variables: EmployeeCount, Over18, StandardHours due to zero variance in sd column of skim() feature output

```{r zero variance variables}
invisible(skim(frito))
#unique(frito$EmployeeCount)
frito2 <- select(frito, -c("EmployeeCount", "Over18", "StandardHours"))
skim(frito2)
ncol(frito2)
```

***
### 3. Remove logically irrelevant variables
- "EmployeeNumber": not related to attrition
- "ID": not related to attrition
- "PerformanceRating" : removed because this is a self given performacne rating and emoloyees would still work towards the best raises even when possibly planning on leaving the company

```{r irrelevant variables}
#skim(frito2)
#view(frito2)

frito3 <- select(frito2, -c("EmployeeNumber", "ID", "PerformanceRating"))
skim(frito3)
ncol(frito3)
view(frito3)
```

***
### 4. Storing all categorical variables as factors
- Confirmed the below variables are stored as factors with skim() function output
  - "Attrition", "BusinessTravel", "Department", "EducationField", "Gender", "JobRole", "MaritalStatus", "Over18", "OverTime"

```{r categorical variables}
# Categorical Variables
skim(frito3)
```

***
### 5. Storing all level numeric variables as factors
- Using the as.factor function to change all level numerical varibales to be stored as factors
  - "JobInvolvement", "EnvironmentSatisfaction", "Education", "JobLevel", "JobSatisfaction", "RelationshipSatisfaction", "StockOptionLevel", "WorkLifeBalance"
```{r level variables}
frito3$Education <- as.factor(frito3$Education)
frito3$EnvironmentSatisfaction <- as.factor(frito3$EnvironmentSatisfaction)
frito3$JobLevel <- as.factor(frito3$JobLevel)
frito3$JobInvolvement <- as.factor(frito3$JobInvolvement)
frito3$JobSatisfaction <- as.factor(frito3$JobSatisfaction)
frito3$RelationshipSatisfaction <- as.factor(frito3$RelationshipSatisfaction)
frito3$StockOptionLevel <- as.factor(frito3$StockOptionLevel)
frito3$WorkLifeBalance <- as.factor(frito3$WorkLifeBalance)

skim(frito3)
ncol(frito3)
```

***
### 6. Checking for highly correlated numeric variables
- Highly correlated relationships
  - Total Working Years v Monthly Income: .78
  - Years at Company v Years in Current Role .78
  - Years at Company v Years with Current Manager .77
  - Years at Company v Total Working Years .64
  - Years at Company v Years Since Last Promotion .64
  - Years with Current Manager v Years in Current Role .71

```{r high correlation}
corrFrito <- frito3

corrFritotable <- corrFrito %>% keep(is.numeric) %>% na.omit %>% cor %>% view

corrFrito %>% keep(is.numeric) %>% na.omit %>% cor %>% corrplot("upper", addCoef.col = "white", number.digits = 2, number.cex = 0.5, method="square", order="hclust", tl.srt=45, tl.cex = 0.8)
invisible(view(corrFritotable))
```

***
#### Correlation Review
- Reviewing the correlated variables we can logically conclude some of these are saying similar things. However, the high correlation doesn't tell the whole story. We will keep investigating to get a better picture of these variables and their importance to Attrition.
  - Keep: "MonthlyIncome", "YearsInCurrentRole", "YearsSinceLastPromotion", "YearsAtCompany", "TotalWorkingYears", "YearsWithCurrManager"
  - Drop: "YearsatCompany"
  
```{r}
skim(frito3)

frito3 <- select(frito3, -c("YearsAtCompany"))
skim(frito3)
ncol(frito3)
```

***
### 7. Numeric v Categorical
- X | Y
- Comparison of Attrition (dependent variable of interest) to categorical variables left in model
- Density plot
  - Colored by Attrition
  - If density plot shows peaks in separate areas then important variable
  - If density plot shows peaks in the same spot (clean overlay) then not an important variable

```{r Numeric v Categorical}
skim(frito3)
```

***
#### Automated EDA: Numeric v  Catgorical

```{r Automated EDA: Numeric v  Catgorical: all at once}
# 1. Name target variable
targetNumCat <- "Attrition"

# 2. Name explanatory variable
numvariables <- frito3 %>% keep(is.numeric) %>% colnames

# 3. Create function
numCatplot <- function(df, explan, resp) {
  ggplot(data = df) + geom_density(aes_string(x = explan, fill = resp), alpha = 0.5) + xlab(explan) + ylab("Attrition")
}

  # Example of working function above
  #numCatplot(frito3, explan =  "TotalWorkingYears", resp = "Attrition")

# 4. Create plot list for plot_grid function to reference
plotlistNumCat <- lapply(numvariables, function(x) numCatplot(frito3, x, targetNumCat))

# 5. Grid of all categorical variables plotted against Attrition
plot_grid(plotlist = plotlistNumCat)
```

***
#### After Numeric v Categorical Review
- Remove variables that have similar trends
    - Telling the same story
    - e.g. "DailyRate", "HourlyRate", "TotalWorkingYears", "MonthlyRate", "YearsWithCurrManager", "YearsAtCompany", "YearsSinceLastPromotion"
- Remove variables that show the Yes and No of Attrition having the same patterns
    - "TrainingTimesLastYear", "PercentSalaryHike", "DistanceFromHome"
- Keep variables that are showing opposite peaks as in the graphs
    - "MonthlyIncome", "YearsInCurrentRole", "NumCompaniesWorked", "Age"

```{r}
skim(frito3)

frito4 <- select(frito3, -c("TrainingTimesLastYear", "PercentSalaryHike", "DistanceFromHome", "DailyRate", "HourlyRate", "TotalWorkingYears", "MonthlyRate", "YearsWithCurrManager", "YearsSinceLastPromotion"))
skim(frito4)
ncol(frito4)
```

***

#### Completed Comparison Analysis
#### Attrition v Age

```{r Attrition v Age}
invisible(frito3 %>% ggplot() + geom_density(aes(x = Age, fill = Attrition, alpha = .1)) +
  theme_excel_new() + ggtitle("Attrition v Age") + ylab("Attrition") + xlab("Age"))
```

***
#### Attrition v Daily Rate

```{r Attrition v Daily Rate}
invisible(frito3 %>% ggplot() + geom_density(aes(x = DailyRate, fill = Attrition, alpha = 0.1)) +
  theme_excel_new() + ggtitle("Attrition v Daily Rate") + ylab("Attrition") + xlab("Daily Rate"))
```

***
#### Attrition v Distance From Home

```{r Attrition v Distance From Home}
invisible(frito3 %>% ggplot() + geom_density(aes(x = DistanceFromHome, fill = Attrition, alpha = 0.1)) +
  theme_excel_new() + ggtitle("Attrition v Distance From Home") + ylab("Attrition") + xlab("Distance From Home"))
```

***
#### Attrition v Hourly Rate

```{r Attrition v Hourly Rate}
invisible(frito3 %>% ggplot() + geom_density(aes(x = HourlyRate, fill = Attrition, alpha = 0.1)) +
  theme_excel_new() + ggtitle("Attrition v Hourly Rate") + ylab("Attrition") + xlab("Hourly Rate"))
```

***
#### Attrition v Monthly Income

```{r Attrition v Monthly Income}
invisible(frito3 %>% ggplot() + geom_density(aes(x = MonthlyIncome, fill = Attrition, alpha = 0.1)) +
  theme_excel_new() + ggtitle("Attrition v Monthly Income") + ylab("Attrition") + xlab("Monthly Income"))
```

***
#### Attrition v Number of Companies Worked

```{r Attrition v Number of Companies Worked}
invisible(frito3 %>% ggplot() + geom_density(aes(x = NumCompaniesWorked, fill = Attrition, alpha = 0.1)) +
  theme_excel_new() + ggtitle("Attrition v Number of Companies Worked") + ylab("Attrition") + xlab("Number of Companies Worked"))
```

***
#### Attrition v Percent Salary Hike

```{r Attrition v Percent Salary Hike}
invisible(frito3 %>% ggplot() + geom_density(aes(x = PercentSalaryHike, fill = Attrition, alpha = 0.1)) +
  theme_excel_new() + ggtitle("Attrition v Percent Salary Hike") + ylab("Attrition") + xlab("Percent Salary Hike"))
```

***
#### Attrition v Years with Current Manager

```{r Attrition v Years with Current Manager}
invisible(frito3 %>% ggplot() + geom_density(aes(x = YearsWithCurrManager, fill = Attrition, alpha = 0.1)) +
  theme_excel_new() + ggtitle("Attrition v Years with Current Manager") + ylab("Attrition") + xlab("Years with Current Manager"))
```

***
#### Attrition v Training Times Last Year

```{r Attrition v Training Times Last Year}
invisible(frito3 %>% ggplot() + geom_density(aes(x = TrainingTimesLastYear, fill = Attrition, alpha = 0.1)) +
  theme_excel_new() + ggtitle("Attrition v Training Times Last Year") + ylab("Attrition") + xlab("Training Times Last Year"))
```

***
#### Attrition v Years in Current Role

```{r Attrition v Years in Current Role}
invisible(frito3 %>% ggplot() + geom_density(aes(x = YearsInCurrentRole, fill = Attrition, alpha = 0.1)) +
  theme_excel_new() + ggtitle("Attrition v Years in Current Role") + ylab("Attrition") + xlab("Years in Current Role"))
```

***
#### Attrition v Years Since Last Promotion

```{r Attrition v Years Since Last Promotion}
invisible(frito3 %>% ggplot() + geom_density(aes(x = YearsSinceLastPromotion, fill = Attrition, alpha = 0.1)) +
  theme_excel_new() + ggtitle("Attrition v Years Since Last Promotion") + ylab("Attrition") + xlab("Years Since Last Promotion"))
```

***
#### Attrition v Total Working Years

```{r Attrition v Total Working Years}
invisible(frito3 %>% ggplot() + geom_density(aes(x = TotalWorkingYears, fill = Attrition, alpha = 0.1)) +
  theme_excel_new() + ggtitle("Attrition v Total Working Years") + ylab("Attrition") + xlab("Years Since Last Promotion"))
```


***
### 8. Categorical v Categorical (Attrition)
- Y | Fill
- Comparison of Attrition (dependent variable of interest) to categorical variables in model
- Bar chart with percentages instead of totals
  - Colored by Attrition
  - If bar chart shows a large difference within the levels/categories of the y variable then it is identified as an important variable to include in the model
  - If bar chart shows a small or zero difference within the levels/categories of the y variable then it is not an important variable to include in the model

```{r Categorical v Categorical (Attrition)}
str(frito4)
frito4 %>% ggplot() + geom_bar(aes(x = Education, fill = Attrition), position = "fill", alpha = 0.9) + coord_flip()
```

***
#### Automated EDA: Categorical v Categorical (Attrition) all at once

```{r Automated EDA: Categorical v Categorical (Attrition) all at once}
# 1. Name target variable
targetCatCat1 <- "Attrition"

# 2. Name explanatory variable
explanatory1 <- frito4 %>% keep(is.factor) %>% colnames

# 3. Create function
numCatCat1 <- function(df, explanatory, response) {
  ggplot(data = df) +geom_bar(aes_string(x = explanatory, fill = response), position = "fill", alpha = 0.9) + coord_flip() + xlab(explanatory)
}

  # Example of working function above
  #numCatCat(frito4, explanatory = "Education", response = "Attrition")


# 4. Create plot list for plot_grid function to reference
plotlistCatCat1 <- lapply(explanatory1, function(x) numCatCat1(frito3, x, targetCatCat1))

# 5. Grid of all categorical variables plotted against Attrition
plot_grid(plotlist = plotlistCatCat1)
```

***
#### After Categorical v Categorical Review
- Remove variables that show a small | zero difference within the levels/categories of the y variable
    - "BusinessTravel", "Department", "Education", "EducationField", "EnvironmentSatisfaction", "Gender", "JobRole", "JobSatisfaction", "MartialStatus", "RelationshipSatisfaction", "JobLevel"
- Keep variables that show a large difference within the levels/categories of the y variable
    - "JobInvolvement", "WorkLifeBalance", "Overtime", "StockOptionLevel"

```{r}
#skim(frito4)

frito5 <- select(frito4, -c("BusinessTravel", "Department", "Education", "EducationField", "EnvironmentSatisfaction", "Gender", "JobRole", "JobSatisfaction", "MaritalStatus", "RelationshipSatisfaction", "JobLevel"))
#skim(frito5)
ncol(frito5)

#view(frito5)
#str(frito5)
frito6 <- frito5 %>% 
  mutate(OverTime = ifelse(OverTime == "No", 0, 1))
frito6 <- frito5 %>%
  mutate(Attrition = ifelse(Attrition ==  "No", 0, 1))
#view(frito6)
```


***
### 9. KNN Model Variables to Reduce Variables
- Categorical: "JobInvolvement", "JobLevel", "OverTime", "StockOptionLevel", "WorkLifeBalance"
- Numerical: "Age", "MonthlyIncome", "NumCompaniesWorked", "YearsInCurrentRole"

### Review of multiple models
```{r}
set.seed(8)
splitPerc = .8
trnIndFrito = sample(1:dim(frito6)[1], round(splitPerc * dim(frito6)[1]))

trainFrito = frito6[trnIndFrito,]

testFrito = frito6[-trnIndFrito,]
```

#### 1. Age, Job Involvement, Job Level

```{r}
#invisible(knn(trainFrito[,c(1,3,4)], testFrito[,c(1,3,4)], trainFrito$Attrition, prob = TRUE, k=19))
#classificationFrito = knn(trainFrito[,c(1,3,4)], testFrito[,c(1,3,4)], trainFrito$Attrition, prob = TRUE, k=19)
#CMFrito1.1 = confusionMatrix(table(testFrito$Attrition, classificationFrito))
#CMFrito1.1
```




#### 2. Job Involvement, Monthly Income, Number Companies Worked

```{r Job Involvement, Monthly Income, Number Companies Worked}
#invisible(knn(trainFrito[,c(3,4,5)], testFrito[,c(3,4,5)], trainFrito$Attrition, prob = TRUE, k=19))
#classificationFrito = knn(trainFrito[,c(3,4,5)], testFrito[,c(3,4,5)], trainFrito$Attrition, prob = TRUE, k=19)
#CMFrito2 = confusionMatrix(table(testFrito$Attrition, classificationFrito))
#CMFrito2
```

#### 3. Monthly Income, Number of Companies Worked, Over Time

```{r Monthly Income, Number of Companies Worked}
#invisible(knn(trainFrito[,c(4,5,6)], testFrito[,c(4,5,6)], trainFrito$Attrition, prob = TRUE, k=7))
#classificationFrito = knn(trainFrito[,c(4,5,6)], testFrito[,c(4,5,6)], trainFrito$Attrition, prob = TRUE, k=7)
#CMFrito3 = confusionMatrix(table(testFrito$Attrition, classificationFrito))
#CMFrito3
```

#### 4. Number of Companies Worked, Over Time, Stock Option Level

```{r Number of Companies Worked, Over Time, Stock Option Level}
#invisible(knn(trainFrito[,c(5,6,7)], testFrito[,c(5,6,7)], trainFrito$Attrition, prob = TRUE, k=7))
#classificationFrito = knn(trainFrito[,c(5,6,7)], testFrito[,c(5,6,7)], trainFrito$Attrition, prob = TRUE, k=7)
#CMFrito5 = confusionMatrix(table(testFrito$Attrition, classificationFrito))
#CMFrito5
```

#### 5. Over Time, WorkLifeBalance, Years In Current Role

```{r}
#invisible(knn(trainFrito[,c(6,7,8)], testFrito[,c(6,7,8)], trainFrito$Attrition, prob = TRUE, k=7))
#classificationFrito = knn(trainFrito[,c(6,7,8)], testFrito[,c(6,7,8)], trainFrito$Attrition, prob = TRUE, k=7)
#CMFrito6 = confusionMatrix(table(testFrito$Attrition, classificationFrito))
#CMFrito6
```


#### 6. Stock Option Level, Work Life Balance, Age

```{r}
#invisible(knn(trainFrito[,c(7,8,1)], testFrito[,c(7,8,1)], trainFrito$Attrition, prob = TRUE, k=7))
#classificationFrito = knn(trainFrito[,c(7,8,1)], testFrito[,c(7,8,1)], trainFrito$Attrition, prob = TRUE, k=7)
#CMFrito7 = confusionMatrix(table(testFrito$Attrition, classificationFrito))
#CMFrito7
```

#### 7. Work Life Balance, Years in Current Role, Age

```{r}
#invisible(knn(trainFrito[,c(8,1,3)], testFrito[,c(8,1,3)], trainFrito$Attrition, prob = TRUE, k= 19))
#classificationFrito = knn(trainFrito[,c(8,1,3)], testFrito[,c(8,1,3)], trainFrito$Attrition, prob = TRUE, k= 19)
#CMFrito8 = confusionMatrix(table(testFrito$Attrition, classificationFrito))
#CMFrito8
```

#### 8. Montly Income (4) Over Time(6) Stock Option Level (7)
```{r}
#invisible(knn(trainFrito[,c(4,6,7)], testFrito[,c(4,6,7)], trainFrito$Attrition, prob = TRUE, k=19))
#classificationFrito = knn(trainFrito[,c(4,6,7)], testFrito[,c(4,6,7)], trainFrito$Attrition, prob = TRUE, k=19)
#CMFrito8 = confusionMatrix(table(testFrito$Attrition, classificationFrito))
#CMFrito8
```



#### Find best k for Model 7
- Best k: 15 - 23
```{r find best k}
set.seed(8)
splitPerc = .8
trnIndFrito = sample(1:dim(frito6)[1], round(splitPerc * dim(frito6)[1]))

trainFrito = frito6[trnIndFrito,]

testFrito = frito6[-trnIndFrito,]

spec = data.frame(specificity = numeric(30), k = numeric(30))
for (i in 1:30) 
  {
  classificationFrito = knn(trainFrito[,c(8,1,3)], testFrito[,c(8,1,3)], trainFrito$Attrition, prob = TRUE, k=i)
  table(testFrito$Attrition, classificationFrito)
  CMFrito8 = confusionMatrix(table(testFrito$Attrition, classificationFrito))
  spec$specificity[i] = CMFrito8$byClass[2]
  spec$k[i] = i
}
plot(spec$k, spec$specificity, type = "l", xlab = "k")
#k <- which.max(spec$specificity)
```

***
#### Final Model (7)

```{r}
invisible(knn(trainFrito[,c(8,1,3)], testFrito[,c(8,1,3)], trainFrito$Attrition, prob = TRUE, k= 19))
classificationFrito = knn(trainFrito[,c(8,1,3)], testFrito[,c(8,1,3)], trainFrito$Attrition, prob = TRUE, k= 19)
CMFrito8 = confusionMatrix(table(testFrito$Attrition, classificationFrito))
CMFrito8
```

***
## Final KNN Prediction Model for Attrition
- Attrition is most closely identified by taking into account
  1. Number of companies a person has worked.
  2. If they do or do not have to work overtime.
  3. An employee's stock option level
- Accuracy > 80%
- Sensitivity > 80%
- Specificity = 75%

***
## Competition Set Analysis
```{r}
competition <- read.csv("https://raw.githubusercontent.com/JaclynCoate/MDS-6306-Doing-Data-Science-Fall-2019/Master/Unit%2014%20and%2015%20Case%20Study%202/CaseStudy2CompSet%20No%20Attrition.csv", header = TRUE, strip.white=TRUE)
invisible(competition)
```

## KNN Model Used to Predict Attrition
```{r}
#Work Life Balance, Years in Current Role, Age
competition <- select(competition, c("ID", "WorkLifeBalance", "YearsInCurrentRole", "Age"))

estimates <- data.frame(knn(trainFrito[,c(8,1,3)], competition[,c(2,3,4)], trainFrito$Attrition, prob = TRUE, k = 19))
compFinal <- cbind(competition, estimates)
colnames(compFinal)[5] <- "Attrition"

compFinal <- compFinal %>% 
  mutate(Attrition = ifelse(Attrition == 0, "No", "Yes"))
invisible(compFinal)
```

### Checking model results aginst graphical analysis

```{r}
compFinal %>% ggplot(mapping = aes(x = Attrition)) + geom_bar() + ggtitle("Comeptition Set: Attrition Count") + theme_excel_new()

frito %>% ggplot(mapping = aes(x = Attrition)) + geom_bar() + ggtitle("Original Data: Attrition Count") + theme_excel_new()
```

### Checking model results aginst graphical analysis

```{r}
compFinal %>% ggplot() + geom_density(aes(x = Age, fill = Attrition, alpha = .1)) +
  theme_excel_new() + ggtitle("Attrition v Age") + ylab("Attrition") + xlab("Age")
```

### Checking model against graphical analysis

```{r}
compFinal %>% ggplot() + geom_bar(aes(x = WorkLifeBalance, fill = Attrition), position = "fill", alpha = .7) + coord_flip()
```

### Write CSV of fitted Competition Data Set
```{r}
#write_csv(compFinal, "/Users/Jaco/Desktop/SMU/Fall2019/DS_6306_Doing_Data_Science/Unit_14CaseStudy2\\CompetitionSet.csv")
```

# Things I had to walk away from
#### Trying to mean of all three variables

```{r}
#iterations = 100
#numks = 100 
#masterAcc = matrix(nrow = iterations, ncol = numks)
#for(j in 1:iterations) {
#  accs = data.frame(accuracy = numeric(numks), k = numeric(numks))
#  trnIndFrito = sample(1:dim(frito6)[1], round(splitPerc * dim(frito6)[1]))
#  trainFrito = frito6[trnIndFrito,]
#  testFrito = frito6[-trnIndFrito,]
#  for(i in 1:numks) {
#    classificationFrito = knn(trainFrito[,c(8,1,3)], testFrito[,c(8,1,3)], trainFrito$Attrition, prob = TRUE, k=i)
#    table(testFrito$Attrition, classificationFrito)
#    CMFrito8 = confusionMatrix(table(testFrito$Attrition, classificationFrito))
#    masterAcc[j,i] = CMFrito8$overall[1]
#  }
#}

#MeanAcc = colMeans(masterAcc)
#plot(seq(1,numks,1),MeanAcc, type = "l")
#k <- which.max(MeanAcc)

#@@@@@@@@@@@@@@@@@@

#iterations = 500
#masterAcc = matrix(nrow = iterations)
#masterSen = matrix(nrow = iterations)
#masterSpec = matrix(nrow = iterations)
#splitPer = .7
#for (j in 1:iterations)
#  {
#  trnIndFrito = sample(1:dim(frito6)[1],round(splitPerc * dim(frito6)[1]))
#  trainFrito = frito6[trnIndFrito,]
#  testFrito = frito6[-trnIndFrito,]
#  
#  classificationFrito = knn(trainFrito[,c(8,1,3)], testFrito[,c(8,1,3)], trainFrito$Attrition, prob = TRUE, k=i)
#  table(testFrito$Attrition, classificationFrito)
#  
#  CMFritoInt = confusionMatrix(table(testFrito$Attrition, classificationFrito))
#  masterAcc[j] = CMFritoInt$overall[1]
#  masterSen[j] = CMFritoInt$byClass[1]
#  masterSpec[j] = CMFritoInt$byClass[2]
#}

#MeanAccUFrit = colMeans(masterAcc)
#MeanAccUFrit
#MeanSenFrit = colMeans(masterSen)
#MeanSenFrit
#MeanSpecFrit = colMeans(masterSpec)
#MeanSpecFrit
```  




### 10. NaiveBates Model to Reduce Variables
- Categorical: "JobInvolvement", "JobLevel", "OverTime", "StockOptionLevel", "WorkLifeBalance"
- Numerical: "Age", "MonthlyIncome", "NumCompaniesWorked", "YearsInCurrentRole"

#### 1. All Variable

```{r}
#set.seed(4)
#splitPerc = .7
#trnIndFrito = sample(1:dim(frito5)[1], round(splitPerc * dim(frito5)[1]))
#trnIndFrito

#trainFrito = frito6[trnIndFrito,]
#trainFrito

#testFrito = frito6[-trnIndFrito,]
#testFrito

#nBfrito1 <- naiveBayes(Attrition ~ . , data = trainFrito)

#predict(nBfrito1, testFrito[,c(1,3,4)], type = "raw")

#table(predict(nBfrito1, testFrito[,c(1,3,4)], type = "raw"), testFrito$Attrition)






#modelU7.s4 <- naiveBayes(Survived ~ . , data =  trainTitanicU7.s4)

#predict(modelU7.s4, testTitanicU7.s4[,c(2,4)], type = "raw")

#table(predict(modelU7.s4, testTitanicU7.s4[,c(2,4)]), testTitanicU7.s4$Survived)

#CMU7.s4 = confusionMatrix(table(predict(modelU7.s4, testTitanicU7.s4[,c(2,4)]), testTitanicU7.s4$Survived))
#CMU7.s4

#knn(trainTitanicU7.s4[,c(2,4)], testTitanicU7.s4[,c(2,4)],trainTitanicU7.s4$Survived, prob = TRUE, k = 11)
#classKNN.s4 = knn(trainTitanicU7.s4[,c(2,4)], testTitanicU7.s4[,c(2,4)],trainTitanicU7.s4$Survived, prob = TRUE, k = 11)
#CMknnU7.s4 = confusionMatrix(table(testTitanicU7.s4$Survived, classKNN.s4))
#CMknnU7.s4
```

```{r}
```

```{r}
```

