---
title: "Job Role Trends"
author: "Jaclyn ! Coate"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::include_graphics("/Users/Jaco/Desktop/SMU/Fall2019/DS_6306_Doing_Data_Science/Unit_14CaseStudy2")
#, results='hide'
```

```{r}
library(tidyverse)
library(skimr)
library(cowplot)
library(ggthemes)
```

```{r data, results='hide'}
job <- read.csv("https://raw.githubusercontent.com/JaclynCoate/MDS-6306-Doing-Data-Science-Fall-2019/Master/Unit%2014%20and%2015%20Case%20Study%202/CaseStudy2-data.csv", header = TRUE, strip.white=TRUE)
invisible(job)
invisible(ncol(job))
invisible(skim(job))
```

```{r grouped variables}
#Categorical:
# "Attrition", "Department", "BusinessTravel", "EducationField", "Gender", "JobRole", "MaritalStatus", "Over18", "OverTime"

# Level
# "JobInvolvement", "EnvironmentSatisfaction", "Education", "JobLevel", "JobSatisfaction", "PerformanceRating", "RelationshipSatisfaction", "StockOptionLevel", "WorkLifeBalance"

#Continuous: 
# "Age", "DailyRate", "DistanceFromHome", "EmployeeCount", "HourlyRate", "MonthlyIncome", "MonthlyRate", "NumCompaniesWorked", "StandardHours" "PercentSalaryHike", "TotalWorkingYears", "TrainingTimesLastYear", "YearsAtCompany", "YearsInCurrentRole", "YearsSinceLastPromotion", "YearsWithCurrManager"

# All Variables
# "Attrition", DailyRate", "Department", "DistanceFromHome", "Education", "EducationField", "EmployeeCount", "EnvironmentSatisfaction", "Gender", "HourlyRate", "JobInvolvement", "JobLevel", "JobRole", "JobSatisfaction", "MaritalStatus", "MonthlyIncome",  "MonthlyRate", "NumCompaniesWorked", "Over18", "OverTime", "PercentSalaryHike", "PerformanceRating", "RelationshipSatisfaction", "StandardHours", "StockOptionLevel", "TotalWorkingYears", "TrainingTimesLastYear", "WorkLifeBalance", "YearsAtCompany", "YearsInCurrentRole", "YearsSinceLastPromotion", "YearsWithCurrManager"
```

```{r as factors}
job$Education <- as.factor(job$Education)
job$EnvironmentSatisfaction <- as.factor(job$EnvironmentSatisfaction)
job$JobLevel <- as.factor(job$JobLevel)
job$JobInvolvement <- as.factor(job$JobInvolvement)
job$JobSatisfaction <- as.factor(job$JobSatisfaction)
job$RelationshipSatisfaction <- as.factor(job$RelationshipSatisfaction)
job$StockOptionLevel <- as.factor(job$StockOptionLevel)
job$WorkLifeBalance <- as.factor(job$WorkLifeBalance)

#skim(job)
```

# Job Role Trends
## Categorical v Categorical
- After reviewing the categorical variables to compare to our Job Roles the below would be insightful for our clients
  - Attrition, OverTime, Job Satisfaction

```{r Categorical v Categorical}
#str(job)
job %>% ggplot() + geom_bar(aes(x = Attrition, fill = JobRole), position = "fill", alpha = 0.9) + coord_flip()

job %>% ggplot() + geom_bar(aes(x = JobSatisfaction, fill = JobRole), position = "fill", alpha = 0.9) + coord_flip()

job %>% ggplot() + geom_bar(aes(x = OverTime, fill = JobRole), position = "fill", alpha = 0.9) + coord_flip()

job %>% ggplot() + geom_bar(aes(x = BusinessTravel, fill = JobRole), position = "fill", alpha = 0.9) + coord_flip()

job %>% ggplot() + geom_bar(aes(x = Gender, fill = JobRole), position = "fill", alpha = 0.9) + coord_flip()

job %>% ggplot() + geom_bar(aes(x = JobInvolvement, fill = JobRole), position = "fill", alpha = 0.9) + coord_flip()

job %>% ggplot() + geom_bar(aes(x = EnvironmentSatisfaction, fill = JobRole), position = "fill", alpha = 0.9) + coord_flip()

job %>% ggplot() + geom_bar(aes(x = PerformanceRating, fill = JobRole), position = "fill", alpha = 0.9) + coord_flip()

job %>% ggplot() + geom_bar(aes(x = WorkLifeBalance, fill = JobRole), position = "fill", alpha = 0.9) + coord_flip()
```

```{r eda of job role v categorical var}
# 1. Name target variable
targetCatCat2 <- "JobRole"

# 2. Name explanatory variable
explanatory2 <- job %>% keep(is.factor) %>% colnames

# 3. Create function
numCatCat2 <- function(df, explanatory, response) {
  ggplot(data = df) + geom_bar(aes_string(x = explanatory, fill = response), position = "fill", alpha = 0.9) + coord_flip() + xlab(explanatory) + ylab("")
}

  # Example of working function above
  #numCatCat(job, explanatory = "Education", response = "Attrition")


# 4. Create plot list for plot_grid function to reference
plotlistCatCat2 <- lapply(explanatory2, function(x) numCatCat2(job, x, targetCatCat2))

# 5. Grid of all categorical variables plotted against Attrition
plot_grid(plotlist = plotlistCatCat2)
```

## Categorical v Numeric
- After reviewing the numeric variables to compare to our Job Roles the below would be insightful for our clients
  - Age, Years Since Last Promotion, Distance from Home, Years At Company

```{r Job Role v Age}
job %>% ggplot() + geom_boxplot(aes(x = JobRole, y = Age, fill = JobRole)) +
  theme_excel_new() + ggtitle("Job Role v Age") + ylab("Education")
```

```{r Job Role v Years Since Last Promotion}
job %>% ggplot() + geom_boxplot(aes(x = JobRole, y = YearsSinceLastPromotion, fill = JobRole)) +
  theme_excel_new() + ggtitle("Job Role v Years Since Last Promotion") 
```

```{r Job Role v Distance from Home}
job %>% ggplot() + geom_boxplot(aes(x = JobRole, y = DistanceFromHome, fill = JobRole)) +
  theme_excel_new() + ggtitle("Job Role v Distance from Home")
```

```{r Job Role v Years At Company}
job %>% ggplot() + geom_boxplot(aes(x = JobRole, y = YearsAtCompany, fill = JobRole)) +
  theme_excel_new() + ggtitle("Job Role v Years At Company")
```
